Parsing Postfix log files

### 2007-07-22 doc/logparser.tex
Converted line endings.
Documented the last aborted delivery attempts.

>>>>

\subsubsection{Yet more aborted delivery attempts}

\label{yet-more-aborted-delivery-attempts}

The aborted delivery attempts described in
section~\ref{aborted-delivery-attempts} occur frequently, but the aborted
delivery attempts described in this section only occur four times in the 93
log files used for testing.  The symptoms are the same as in
section~\ref{aborted-delivery-attempts}, except that there \textit{is\/} a
\texttt{postfix/cleanup} log line; there does not appear to be anything in
the log file to explain why there are no further log messages.  The only
way to detect these mails is to periodically scan all mails in the state
tables, deleting any mails displaying the following characteristics:

    \item The timestamp of the last log line for the mail must be 12 hours
        or more earlier than the last log line parsed.

    \item There must be exactly two \texttt{postfix/smtpd} and one
        \texttt{postfix/cleanup} log entries for the mail, with no
        additional log entries.

12 hours is a somewhat arbitrary time period, but it is far longer than
Postfix would delay delivery of a mail in the queue.  The state tables are
scanned for mails matching the characteristics above each time the end of a
log file is reached, and matching mails are deleted.
